---
title: "Insecticide Resistance Management : prototype game scenarios v4 annual with daily timestep"
author: "Andy South"
date: "`r Sys.Date()`"
#output: rmarkdown::html_vignette
# trying to increase width fails
#  width: "110" 
#to produce a pdf
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{IRM-prototype-game-scenarios3}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This document demonstrates how annual scenarios for vector populations and resistance can be generated from a few simple equations.


The game will modify input parameters to generate reasonable scenarios. The input parameters are simply a means to generate reasonable scenarios.


In the following plots time in days is represented on the x axis, the top panel shows insecticide use, the middle panel shows vector population and the lower panel shows resistance (phenotypic). 

The code included is there merely to show us as developers how the scenarios were generated.


For an interactive version of the equations used to generate these plots see [https://andysouth.shinyapps.io/shinyGame4](https://andysouth.shinyapps.io/shinyGame4).


```{r, eval=TRUE, echo=FALSE, message=FALSE}
#### load required packages
require(resistanceGame)
```

\newpage

## scenario 1 : no insecticide use
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
plot_sim( run_sim(num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 2 : continuous pyr use in presence of resistance
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
l_config <- read_config()
l_config2 <- config_plan(l_config, t_strt=1, t_stop=360, control_id='irs_pyr')
plot_sim( run_sim(l_config=l_config2, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 3 : continuous use of ops with no resistance
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
l_config2 <- config_plan(l_config, t_strt=1, t_stop=360, control_id='irs_ops')
plot_sim( run_sim(l_config=l_config2, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 4 : pyr used for 6 months
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
l_config2 <- config_plan(l_config, t_strt=1, t_stop=180,
                            control_id='irs_pyr')
plot_sim( run_sim(l_config=l_config2, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 5 : ops for 6 months
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
l_config2 <- config_plan(l_config, t_strt=1, t_stop=180, control_id=c('irs_ops'))
plot_sim( run_sim(l_config=l_config2, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 6 : 6 months pyr, 6 months ops
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
l_config2 <- config_plan(l_config, t_strt=c(1,181), t_stop=c(180,360),
                            control_id=c('irs_pyr','irs_ops'))
plot_sim( run_sim(l_config=l_config2, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 7 : 6 months pyr, 6 months ddt
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
l_config2 <- config_plan(l_config, t_strt=c(1,181), t_stop=c(180,360),
                            control_id=c('irs_pyr','irs_ddt'))
plot_sim( run_sim(l_config=l_config2, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 8 : no insecticide use, 50% randomness added
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
plot_sim( run_sim(randomness=0.5, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 9 : same as previous but just a different randomisation
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
plot_sim( run_sim(randomness=0.5, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 10 : no insecticide use, 10% randomness added
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
plot_sim( run_sim(randomness=0.1, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 11 : continuous pyr use, resistance_modifier < 1 decreases effect of resistance
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
l_config2 <- config_plan(l_config, t_strt=1, t_stop=360, control_id='irs_pyr')
plot_sim( run_sim(l_config=l_config2, resistance_modifier=0.1, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 12 : continuous pyr use, resistance_modifier > 1 increases effect of resistance
```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
plot_sim( run_sim(l_config=l_config2, resistance_modifier=10, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )
```

\newpage

## scenario 13 : set a different control and resistance mechanism and control plan

```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
l_config2 <- config_controls(l_config, control_id='new_ai', vector_id='an_gamb',
                             control_kill_rate=0.4)
l_config2 <- config_resistances(l_config2, control_id='new_ai', resistance_id="target_site",
                                resistance_strength=0.8,
                                resistance_incr=0.2,
                                resistance_decr=0.1)
l_config2 <- config_plan(l_config2, t_strt=1, t_stop=360, control_id='new_ai')
plot_sim( run_sim(l_config=l_config2, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01) )

```

\newpage

## scenario 14 : change emergence over time (6 tstep(month) cycle).

```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
emergence = c(rep(0.3,180),rep(0,180))
plot_sim( run_sim(emergence=emergence, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01), plot_emergence=TRUE )
```

\newpage

## scenario 15 : emergence gradual change.

```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
#sin curve to create a gradual change from 0 to 0.3
emergence = 0.3*sin(seq(0,3.1,0.01))
plot_sim( run_sim(emergence=emergence, num_tsteps=360, resist_incr=0.02, resist_decr = 0.01), plot_emergence=TRUE )
```

\newpage

## scenario 16 : emergence annual pattern of monthly values, daily time step

```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
emergence = c(rep(0.3,180),rep(0,180))
plot_sim( run_sim(num_tsteps=360,emergence=emergence, survival=0.7,
                  resist_incr=0.02, resist_decr = 0.01), 
          plot_emergence=TRUE )
```

\newpage

## scenario 17 : as previous, with control

```{r, eval=TRUE, echo=TRUE, message=FALSE, results='hide', fig.width=7, fig.height=6}
emergence = c(rep(0.3,180),rep(0,180))
l_config2 <- config_plan(l_config, t_strt=c(1,181), t_stop=c(180,360),
                         control_id=c('irs_ops','irs_pyr'))
plot_sim( run_sim(l_config=l_config2, 
                  num_tsteps=360, emergence=emergence, survival=0.7,
                  resist_incr=0.02, resist_decr = 0.01), 
          plot_emergence=TRUE )
```

\newpage



## How controls and resistance mechanisms can be specified.

Our generic approach allows us to specify any combination of controls and resistance mechanisms. The controls cause a specified kill rate(s) on specified vector(s). The resistance mechanisms specify which controls they apply to and how fast resistance increases and decreases in the presence and absence respectively of that control. Cross resistance can be specified simply by specifiying multiple controls for one resistance mechanism.

The relationships between vectors, controls and resistance mechanisms are specified in simple configuration files. Here is a simple example of a collection of such configuration files :

#### places.csv
```{r, eval=TRUE, echo=FALSE, message=FALSE, results='markup', fig.width=7, fig.height=6}
places <- read.csv( system.file('extdata','config1','places.csv', package='resistanceGame'))
print(places) 
```    

#### vectors.csv
```{r, eval=TRUE, echo=FALSE, message=FALSE, results='markup', fig.width=7, fig.height=6}
vectors <- read.csv( system.file('extdata','config1','vectors.csv', package='resistanceGame'))
print(vectors)
```

#### controls.csv
```{r, eval=TRUE, echo=FALSE, message=FALSE, results='markup', fig.width=7, fig.height=6}
controls <- read.csv( system.file('extdata','config1','controls.csv', package='resistanceGame'))
print(controls)
```

#### resistances.csv
```{r, eval=TRUE, echo=FALSE, message=FALSE, results='markup', fig.width=7, fig.height=6}
resistances <- read.csv( system.file('extdata','config1','resistances.csv', package='resistanceGame'))
print(resistances)
```

#### control_plan.csv
```{r, eval=TRUE, echo=FALSE, message=FALSE, results='markup', fig.width=7, fig.height=6}
control_plan <- read.csv( system.file('extdata','config1','control_plan.csv', package='resistanceGame'))
print(control_plan)
```

